% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}

\documentclass[]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi

% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
  \usepackage{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
  \usepackage[left=2.5in,bottom=1.25in,top=1.25in,right=1in]{geometry}
  \ifxetex
\usepackage[setpagesize=false, % page size defined by xetex
            unicode=false, % unicode breaks when used with xetex
            xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
bookmarks=true,
pdfauthor={},
pdftitle={Preregistration for my Healthy Beaches Living Data Mini-project},
colorlinks=true,
citecolor=blue,
urlcolor=blue,
linkcolor=magenta,
pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}

% Customization for cos_prereg
\usepackage{longtable,booktabs,threeparttable,tabularx}
\linespread{1.5}
\newcounter{question}
\setcounter{question}{0}

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

%%% Change title format to be more compact
\usepackage{titling}

\def\changemargin#1#2{\list{}{\rightmargin#2\leftmargin#1}\item[]}
\let\endchangemargin=\endlist

\setlength{\droptitle}{-2em}
\title{Preregistration for my Healthy Beaches Living Data Mini-project}
\pretitle{\begin{changemargin}{-8pc}{0pc} \centering\large Preregistration\\ \Huge}
\posttitle{\end{changemargin}}
  \author{
          Laura Schnell\textsuperscript{1}          \\ \vspace{0.5cm}
              \textsuperscript{1} University of Regina      }

  \def\affdep{{""}}%
  \def\affcity{{""}}%
  \preauthor{\begin{changemargin}{-8pc}{0pc} \centering\large}
  \postauthor{\end{changemargin}}
\date{24. September 2023}
\predate{\begin{changemargin}{-8pc}{0pc} \centering\large\emph}
\postdate{\end{changemargin}}
\usepackage{fancyhdr}
\pagestyle{fancy}
\setlength{\headheight}{14.0pt}
\renewcommand{\headrulewidth}{0pt}
\lhead{}
\rhead{\large\textsc{\MakeLowercase{Healthy Beaches preregistration}}}



% Title settings
\usepackage{titlesec}
\titleformat{\section}[display]{\bfseries\Large}{\thesection}{}{}[]
\titlespacing{\section}{0pc}{*3}{*1.5}
\titleformat{\subsection}[leftmargin]{\titlerule\bfseries\filleft}{\thesubsection}{.5em}{}
\titlespacing{\subsection}{8pc}{5ex plus .1ex minus .2ex}{1.5pc}


% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi


\begin{document}
\maketitle
\vspace{2pc}


\ifPDFTeX
  \newcommand\Question[2]{%
   \leavevmode\par
   \stepcounter{question}
   \noindent
   \textbf{\thequestion. #1}. #2\par}
\else % if luatex or xetex
  \NewCommandCopy{\oldQuestion}{\Question}
  \renewcommand\Question[2]{%
   \leavevmode\par
   \stepcounter{question}
   \noindent
   \textbf{\thequestion. #1}. #2\par}
\fi



\newcommand\Answer[1]{%
    \noindent
    \textit{Registered response}: #1\par}

\hypertarget{data-collection}{%
\subsection{Data collection}\label{data-collection}}

\textbf{It's complicated.} Data has been collected by the Saskatchewan
Department of Health through their Healthy Beaches program and is
available at the following link. I aim to collect this data from the
Healthy Beaches website, convert it into a .csv, and use it for
exploratory analysis.

\hypertarget{hypothesis}{%
\subsection{Hypothesis}\label{hypothesis}}

\begin{quote}
This work is exploratory but my starting hypothesis is that E. coli and
microcystin levels measured by the Healthy Beaches Program {[}1{]} will
fluctuate over the course of the summer. This dataset only includes
date, location, and E. coli and microcystin levels so I cannot test any
potential relationships should there be fluctuations, but I would expect
both temperature and beach use have an impact on microbial growth in
beachwater {[}2, 3{]}.
\end{quote}

\hypertarget{dependent-variable}{%
\subsection{Dependent variable}\label{dependent-variable}}

\begin{quote}
E. coli levels were measured by the Healthy Beaches Program in colony
forming units (CFU) per 100 mL. Collected water was cultured selectively
for coliforms by the Roy Romanow Provincial Laboratory (RRPL).
Microcystin levels are measured using enzyme-linked immunosorbent assay
that is performed on the collected water, again by RRPL.
\end{quote}

\hypertarget{conditions}{%
\subsection{Conditions}\label{conditions}}

\begin{quote}
Time is the only fluctuating condition. Sampling is performed yearly
from May to August. I have sourced data from the Healthy Beaches website
from 2019, 2020, 2022, and 2023.
\end{quote}

\hypertarget{analyses}{%
\subsection{Analyses}\label{analyses}}

\begin{quote}
Data quality checks will be performed using the lubridate and tidyverse
R packages. Exploratory data visualization will be performed with
ggplot2. No modelling will be performed because there is insufficient
data.
\end{quote}

\hypertarget{outliers-and-exclusions}{%
\subsection{Outliers and exclusions}\label{outliers-and-exclusions}}

\begin{quote}
Outliers will only be excluded from analyses if there is a note in the
Healthy Beaches data files that note something odd happened with the
water testing. Otherwise, outliers will be defined as unexpected or
atypical E. coli or microcystin levels and left alone.
\end{quote}

\hypertarget{sample-size}{%
\subsection{Sample size}\label{sample-size}}

\begin{quote}
Data from 2019, 2020, 2022, and 2023 will be used with the most sampled
lake and recreational areas as the main focus.
\end{quote}

\hypertarget{other}{%
\subsection{Other}\label{other}}

\begin{quote}
This project is exploratory analysis on already existing data gathered
by the Saskatchewan Health Authority Healthy Beaches program.
\end{quote}

\hypertarget{study-type}{%
\subsection{Study type}\label{study-type}}

Finally. For record keeping purposes, please tell us the type of study
you are pre-registering.

\begin{itemize}
\tightlist
\item
  Class project or assignment
\end{itemize}

\hypertarget{references}{%
\section{References}\label{references}}

\begin{quote}
\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Government of Saskatchewan. ``Healthy Beaches Program \textbar{}
  Environmental Health.'' Accessed September 24, 2023.
  \url{https://www.saskatchewan.ca/residents/environment-public-health-and-safety/environmental-health/healthy-beach-program}.
\end{enumerate}
\end{quote}

\begin{quote}
\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{1}
\tightlist
\item
  Weiskerger, Chelsea J., João Brandão, Warish Ahmed, Asli Aslan,
  Lindsay Avolio, Brian D. Badgley, Alexandria B. Boehm, et
  al.~``Impacts of a Changing Earth on Microbial Dynamics and Human
  Health Risks in the Continuum between Beach Water and Sand.'' Water
  Research 162 (October 1, 2019): 456--70.
  \url{https://doi.org/10.1016/j.watres.2019.07.006}.
\end{enumerate}
\end{quote}

\begin{quote}
\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{2}
\tightlist
\item
  Zhou, Chuangchuang, Hui Chen, Haipeng Zhao, and Qiang Wang.
  ``Microcystin Biosynthesis and Toxic Effects.'' Algal Research 55 (May
  1, 2021): 102277. \url{https://doi.org/10.1016/j.algal.2021.102277}.
\end{enumerate}
\end{quote}

\vspace{-2pc}
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{-1in}
\setlength{\parskip}{8pt}

\noindent

\end{document}
